A full approximation storage multilevel method \\ for nonlinear variational inequalities

### 2023-06-17 paper/fascd.tex
half-baked thoughts on icd-tele as another basic CD iteration

@@

>>>>

FIXME \pr{icd-tele} as third basic CD iteration

\begin{pseudofloat}[H]
\begin{pseudo*}
\pr{icd-tele}(w^J)\text{:} \\+
    for $j = 0,\dots,J$: \\+
        \rm{find} $z_j\in \mathcal{U}_j$ \rm{so that for all} $v_j\in \mathcal{U}_j$, \\+
            $\displaystyle \ip{f\Big(w^J + \alpha \sum_{i<j} z_i + \alpha z_j\Big)}{v_j-z_j} \ge \ip{\ell}{v_j-z_j}$ \\--
    return $\tilde w^J=w^J + \alpha \sum_{i\le J} z_i$
\end{pseudo*}
\caption{One telescoping incomplete CD iteration for VI problem \eqref{eq:vi}, assuming $w^J\in\mathcal{K}^J$, property \eqref{eq:fe:finestlevelequivalent}, and incomplete CD \eqref{eq:fe:upwardsuminclusion}.}
\label{alg:basiccd-tele}
\end{pseudofloat}

@@

Compared specifically to the $V(1,0)$ cycle presented as Algorithm 4.7 in \cite{GraeserKornhuber2009}, one might say informally that \pr{fascd-vcycle} is a $V(1,1)$ cycle.  However, its structure relates directly to the basic CD iterations (Sections \ref{sec:cditers}, \ref{sec:cdmultilevel}) as well.  In unilateral cases it is precise to say that one iteration of \pr{fascd-vcycle} is an application of \pr{cd-mult} over CD \eqref{eq:fe:downwardsuminclusion}, using the defect constraint meaning of the downward constraint sets $\mathcal{D}^j$, followed by an application of \pr{icd-tele} over the incomplete CD \eqref{eq:fe:upwardsuminclusion}.  FIXME: idea is that once you are using defect constraints you no longer depend on the literal availability of $\Pi_i$, so incomplete CD suffices, e.g.~even for \pr{cd-mult}
